Think deep for reef resilience

### 2025-09-11 paper/paper_draft.qmd
Update map plotting and figure captions to reverse colour gradients

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median reef depth. Colour-coded areas outline GBR
marine park management regions, where orange represents the Far Northern management region,
green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers
Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for visual clarity.
Lighter colours represent greater reef depth values than darker colours. All 2429 reefs
included in this investigation are represented in this figure. Annotations represent major
coastal settlements along the GBR.](../figs/depth_med_input_map.png){#sfig-depth-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by reef carrying capacity (coral habitable area).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Lighter colours represent greater carrying capacity
area values than darker colours. All 2429 reefs included in this investigation are
represented in this figure. Annotations represent major coastal settlements along the
GBR.](../figs/abs_k_area_input_map.png){#sfig-abs-k-area-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by outgoing connection strength (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Lighter colours represent higher outgoing connection strength values than
darker colours. All 2429 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_out_strength_input_map.png){#sfig-outgoing-conn-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by source-to-sink connectivity ratio (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Lighter colours represent higher source-to-sink
values than darker colours. Source-to-sink ratio values above zero (one on normal scale)
indicate a reef has greater outgoing than incoming connectivity. All 2429 reefs included in
this investigation are represented in this figure. Annotations represent major coastal
settlements along the GBR.](../figs/log_so_to_si_input_map.png){#sfig-sotosi-conn-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by larval retention probability (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Lighter colours represent higher probability of retaining spawned larvae
than darker colours. All 2429 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_self_strength_input_map.png){#sfig-self-conn-map fig-align="center"
width="14.82cm"}

@@

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median number of years exceeding positive carbonate
budget threshold. Colour-coded areas outline GBR marine park management regions, where
orange represents the Far Northern management region, green represents Cairns/Cooktown, red
covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids
are marked individually for visual clarity. Reefs that have a median positive carbonate
budget year value of 0 years are coloured in grey. All other reefs are coloured according to
their median years across threshold values, with lighter colours representing greater number
of years with positive carbonate budgets than darker colours. All 2429 reefs included in
this investigation are represented in this figure. This map depicts values from the
ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by mean time series DHW value. Colour-coded areas
outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Lighter colours represent higher mean DHW values than darker colours. All
2429 reefs included in this investigation are represented in this figure. This map depicts
values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by weighted incoming connectivity levels (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Lighter colours represent higher weighted incoming
connectivity values than darker colours. All 2429 reefs included in this investigation are
represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations
represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map
fig-align="center" width="14.82cm"}

>>>>

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median reef depth. Colour-coded areas outline GBR
marine park management regions, where orange represents the Far Northern management region,
green represents Cairns/Cooktown, red covers Townsville/Whitsunday and blue covers
Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for visual clarity.
Darker colours represent greater reef depth values than lighter colours. All 2429 reefs
included in this investigation are represented in this figure. Annotations represent major
coastal settlements along the GBR.](../figs/depth_med_input_map.png){#sfig-depth-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by reef carrying capacity (coral habitable area).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent greater carrying capacity
area values than lighter colours. All 2429 reefs included in this investigation are
represented in this figure. Annotations represent major coastal settlements along the
GBR.](../figs/abs_k_area_input_map.png){#sfig-abs-k-area-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by outgoing connection strength (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher outgoing connection strength values than
lighter colours. All 2429 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_out_strength_input_map.png){#sfig-outgoing-conn-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by source-to-sink connectivity ratio (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent higher source-to-sink
values than lighter colours. Source-to-sink ratio values above zero (one on normal scale)
indicate a reef has greater outgoing than incoming connectivity. All 2429 reefs included in
this investigation are represented in this figure. Annotations represent major coastal
settlements along the GBR.](../figs/log_so_to_si_input_map.png){#sfig-sotosi-conn-map
fig-align="center" width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by larval retention probability (Log10). Colour-coded
areas outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher probability of retaining spawned larvae
than lighter colours. All 2429 reefs included in this investigation are represented in this
figure. Annotations represent major coastal settlements along the
GBR.](../figs/log_self_strength_input_map.png){#sfig-self-conn-map fig-align="center"
width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by median number of years exceeding positive carbonate
budget threshold. Colour-coded areas outline GBR marine park management regions, where
orange represents the Far Northern management region, green represents Cairns/Cooktown, red
covers Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids
are marked individually for visual clarity. Reefs that have a median positive carbonate
budget year value of 0 years are coloured in grey. All other reefs are coloured according to
their median years across threshold values, with darker colours representing greater number
of years with positive carbonate budgets than lighter colours. All 2429 reefs included in
this investigation are represented in this figure. This map depicts values from the
ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/median_carbonate_budget_map.png){#sfig-carb-budget-map
fig-align="center" width="14.82cm"}

@@

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by mean time series DHW value. Colour-coded areas
outline GBR marine park management regions, where orange represents the Far Northern
management region, green represents Cairns/Cooktown, red covers Townsville/Whitsunday and
blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are marked individually for
visual clarity. Darker colours represent higher mean DHW values than lighter colours. All
2429 reefs included in this investigation are represented in this figure. This map depicts
values from the ACCESS-ESM1-5 GCM. Annotations represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/mean_dhw_input_map.png){#sfig-mean-dhw-map fig-align="center"
width="14.82cm"}

![Map of the Great Barrier Reef region, including GBRMPA management areas (polygons) and all
considered reefs (points), coloured by weighted incoming connectivity levels (Log10).
Colour-coded areas outline GBR marine park management regions, where orange represents the
Far Northern management region, green represents Cairns/Cooktown, red covers
Townsville/Whitsunday and blue covers Mackay/Capricorn [@GBRMPA2007]. Reef centroids are
marked individually for visual clarity. Darker colours represent higher weighted incoming
connectivity values than lighter colours. All 2429 reefs included in this investigation are
represented in this figure. This map depicts values from the ACCESS-ESM1-5 GCM. Annotations
represent major coastal settlements along the
GBR.](../figs/ACCESS-ESM1-5/weighted_incoming_conn_input_map.png){#sfig-incoming-conn-map
fig-align="center" width="14.82cm"}
